Approximation as Differentiation

### 2025-05-05 appendix/notes/auto-diff.tex
smooth -> differentiable (don't need C^\infinity functions).

\begin{definition}[$\Diff$]
\label{def:auto-diff:Diff}
Define $\Diff_*$ to be the category where the objects are all finite vector spaces $\RR^n$ and the morphisms
are all maps $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$, with $f_1$ differentiable. Composition in
$\Diff_*$ is given by:
\begin{align*}
(g \comp f)_1(x) &= f_1(g_1(x)) \\
(g \comp f)_2(x) &= g_2(f_1(x)) \comp f_2(x)
\end{align*}
\end{definition}

>>>>

\begin{definition}[$\Diff$]
\label{def:auto-diff:Diff}
Define $\Diff_*$ to be the category where the objects are all finite vector spaces $\RR^n$ and the morphisms
are all maps $f: \RR^m \to \RR^n \times (\RR^m \linearto \RR^n)$ with $f_1$ differentiable. Composition in
$\Diff_*$ is given by:
\begin{align*}
(g \comp f)_1(x) &= f_1(g_1(x)) \\
(g \comp f)_2(x) &= g_2(f_1(x)) \comp f_2(x)
\end{align*}
\end{definition}
